### 2021-05-23 code/manuscript.Rmd
revert to buildmer

```{r setup, include=FALSE}
# Load packages
library(emmeans)
library(MASS)
library(afex)
library(reticulate)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)
library(furrr)

@@

@@

  # Compute models for dependent variables in parallel
  dvs <- c("logRT", "P1", "N170", "N400")
  n_cores <- min(length(dvs), availableCores())
  plan("multicore", workers = n_cores)
  future_map(dvs, function(dv, dat = trials) {

    # Define model formula
    form <- paste0(
      dv, " ~ part * condition +
        (part * condition | subject_id) +
        (part * condition | item_id)"
    ) %>% formula()

@@

    # Fit initial model
    fit <- lmer(form, dat, REML = TRUE)

    # Refit using all available optimizers
    fits <- all_fit(fit, formula = form, data = dat)

    # See which of the optimizers converged
    fits_converged <- keep(
      fits,
      ~ .x@optinfo$conv$opt == 0 & length(.x@optinfo$conv$lme4) == 0
    )

    # Find best model via logLik
    logliks <- map(fits_converged, logLik)
    fit_best <- fits[[which.max(logliks)]]

    # Compute follow-up comparisons
    emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
    em <- emmeans(fit_best, specs, infer = TRUE)

    # Return a list of relevant model outputs
    return(
      list(
        fit = fit_best,
        anova = anova(fit_best),
        means = em$emmeans,
        contrasts = em$contrasts,
        all_fits = fits
      )
    )
  }) %>%

    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_freq) -> models_freq

  # Stop the workers
  future:::ClusterRegistry("stop")
}

@@

```{r bayes, eval=FALSE}
library(brms)
options(mc.cores = 6)

data_joint_subs %>%
  filter(condition %in% c("Informed", "Naive")) %>%
  droplevels() %>%
  select(part, condition, participant, item, P1, N170, N400) %>%
  na.omit() %>%
  as.list() -> data_brm

contrasts_condition <- t(cbind(c("Informed" = 1, "Naive" = -1)))
contrasts_part <- t(cbind(c("I" = -1, "II" = 1, "III" = 0), c("I" = 0, "II" = -1, "III" = 1)))
contrasts(data_brm$condition) <- ginv(contrasts_condition)
contrasts(data_brm$part) <- ginv(contrasts_part)

formula <- P1 ~ part / condition + (part / condition | participant) + (part / condition | item)
prior <- set_prior("cauchy(0, 0.707)", class = "b")

mod_brm <- brm(
  formula = formula,
  data = data_brm,
  family = gaussian(),
  prior = prior,
  sample_prior = "yes",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 20000,
  warmup = 2000,
  cores = 4,
  control = list(adapt_delta = 0.9)
)

@@

```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())

>>>>

```{r setup, include=FALSE}
# Load packages
library(MASS)
library(lme4)
library(buildmer)
library(emmeans)
library(brms)
library(parallel)
library(reticulate)
library(papaja)
library(cowplot)
library(scales)
library(tidyverse)
library(magrittr)

@@

# Number of CPU cores for parallel model fitting
n_cores <- detectCores()

@@

  # Compute models for dependent variables in parallel
  dvs <- c("logRT", "P1", "N170", "N400")
  map(dvs, function(dv) {

    # Define model formula
    formula_lme <- paste0(
      dv, " ~ part * condition +
        (part * condition | subject_id) +
        (part * condition | item_id)"
    ) %>% formula()

@@

    # Automic model selection via likelihood ratio tests
    # using an alpha level of .20 (see Matuschek et al., 2017, J Mem Lang)
    cl <- makeCluster(n_cores)
    build <- buildmer(
      formula = formula_lme,
      data = trials,
      buildmerControl = buildmerControl(
        direction = c("backward", "backward"),
        cl = cl,
        crit = "LRT",
        elim = function(logp) exp(logp) >= .20,
        quiet = TRUE,
        calc.anova = TRUE,
        ddf = "Satterthwaite",
        REML = FALSE,
      ),
      control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e6))
    )
    stopCluster(cl)

    # Compute follow-up comparisons
    emm_options(lmer.df = "Satterthwaite", lmerTest.limit = Inf)
    em <- emmeans(build@model, specs, infer = TRUE)

    # Return a list of relevant model outputs
    return(
      list(
        model = build@model,
        anova = build@anova,
        summary = build@summary,
        means = em$emmeans,
        contrasts = em$contrasts
      )
    )
  }) %>%

    # Save
    set_names(dvs) %T>%
    saveRDS(fnames$models_freq) -> models_freq
}

@@

```{r models_bayes, eval=FALSE}
# Define model formula
form <- P1 ~ part * condition +
  (part * condition | subject_id) +
  (part * condition | item_id)

# Default prior for slopes
prior <- set_prior("cauchy(0, 0.707)", class = "b")

# Fit Bayesian mixed model
mod_brm <- brm(
  formula = form,
  data = trials,
  family = gaussian(),
  prior = prior,
  sample_prior = "yes",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  # iter = 20000,
  # warmup = 2000,
  cores = 4,
  backend = "cmdstanr"
)

@@

```{r fig1, include=TRUE, fig.height=11, fig.cap = "(ref:fig1_caption)"}
# Load montage and data
montage <- read_csv(fnames$montage, col_types = cols())
evokeds <- read_csv(fnames$evo_gavg, col_types = cols())
models_freq <- readRDS(fnames$models_freq)
